Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-15 paper/abstract.tex
Minor update to abstract

Cyber-physical systems, such as avionics, must be tolerant to cyber-attacks in the same way they are tolerant to random faults: they either gracefully recover or safely shut down as requirements dictate. The DARPA Cyber Assured Systems Engineering program is developing design, analysis, and verification tools that enable systems engineers to design-in cyber-resiliency in a Model-Based Systems Engineering environment. This paper describes automated model transformations that introduce  high-assurance cyber-resiliency components into a system, in particular filters and monitors that prevent malicious input and detect supply chain attacks, respectively. A formal specification defines each component, and is used to verify that the component addresses system level cyber requirements. Implementations are directly synthesized from their specifications, and are automatically proven to preserve the exact meaning of the specifications all the way down to the binary code level. The model transformations are integrated into the Open Source AADL Tool Environment (OSATE). The paper further reports on a case study applying security-enhancing model transformations to a UAV system that uses the Air Force Research Laboratory's OpenUxAS services for route planning. In the case study, the model transformations add filters to guard against malformed input, as well as monitors to guard against ground station spoofing and malicious flight plans from OpenUxAS.

>>>>

Cyber-physical systems, such as avionics, must be tolerant to cyber-attacks in the same way they are tolerant to random faults: they either gracefully recover or safely shut down as requirements dictate. The DARPA Cyber Assured Systems Engineering program is developing tools for design, analysis, and verification that enable systems engineers to design-in cyber-resiliency in a Model-Based Systems Engineering environment. This paper describes automated model transformations that introduce high-assurance cyber-resiliency components into a system, in particular filters and monitors that prevent malicious input and detect supply chain attacks, respectively. A formal specification defines each high-assurance component, and is used to verify that the component addresses system level cyber requirements. Implementations for these high-assurance components are directly synthesized from their specifications, and are automatically proven to preserve the exact meaning of the specifications all the way down to the binary code level. The model transformations are integrated into the Open Source AADL Tool Environment (OSATE). The paper further reports on a case study applying security-enhancing model transformations to a UAV system that uses the Air Force Research Laboratory's OpenUxAS services for route planning. In the case study, the model transformations add filters to guard against malformed input, as well as monitors to guard against ground station spoofing and malicious flight plans from OpenUxAS.
